Every Author as First Author

### 2023-03-30 paper.tex
Re-organize listings and improve Future Work

@@

@@

Listing~\ref{lst:namestack} shows the source code for this macro.
The main idea is to render each name (into a \TeX\ horizontal box),
and stack them vertically (in a \TeX\ vertical box)
with a negative one-line vertical space in between consecutive names.
The example above effectively becomes:

This main content gets wrapped in three additional components:
%
\begin{enumerate}
\item \lstinline|\texttransparent{0.666}{...}| (from \texttt{transparent.sty})
  to make the names semi-transparent at opacity $2/3$.
  The opacity can also be overridden via an optional argument, as in
  \lstinline|\namestack[0.9]{...}|.
\item \lstinline|\pdftooltip| (from \texttt{pdfcomment.sty})
  to add tooltips to the stack, with the original list of names.
\item \lstinline|\BeginAccSupp{...ActualText=...}...\EndAccSupp{}|
  (from \texttt{accsupp.sty}) to override copy/paste behavior for the stack.
\end{enumerate}

@@

\lstset{
  language=HTML,
  alsoletter={-},
  otherkeywords={grid-row, grid-column, opacity, display, inline-grid},
  emph={stack, name}, % not working because of tag option
  identifierstyle=,
  morecomment=[s]{/*}{*/}
}

\lstinputlisting[caption={HTML source code illustrating a name stack},label=lst:html]{stack.html}

A final issue is that overlapping name stacks are not easy to read.
It may be possible to write names in a way that has no first name
but still makes all names clearly readable.
For example, a circle has no beginning or end, so arranging the names
in a circular pattern avoids arranging any author ``first''.
Figure~\ref{fig:circles} shows some initial experiments in this direction.
It remains unsolved how to fit such circular arrangements
in with the rest of a text document, which feels inherently sequential.

>>>>

% Put figures and text together
\def\textfraction{0.01}
\def\topfraction{0.99}
\def\bottomfraction{0.99}
\def\floatpagefraction{0.99}
\def\dblfloatpagefraction{0.99}

@@

Listing~\ref{lst:namestack} below shows the source code for this macro.
The main idea is to render each name (into a \TeX\ horizontal box),
and stack them vertically (in a \TeX\ vertical box)
with a negative one-line vertical space in between consecutive names.
The example above effectively becomes:

This main content gets wrapped in three additional components:
%
\begin{enumerate}
\item \lstinline|\textopacity{0.666}{...}| (implemented via \texttt{pgf.sty})
  to make each name semi-transparent at opacity $2/3$.
  The opacity can also be overridden via an optional argument, as in
  \lstinline|\namestack[0.9]{...}|.
\item \lstinline|\pdftooltip| (from \texttt{pdfcomment.sty})
  to add tooltips to the stack, with the original list of names.
\item \lstinline|\BeginAccSupp{...ActualText=...}...\EndAccSupp{}|
  (from \texttt{accsupp.sty}) to override copy/paste behavior for the stack.
\end{enumerate}

\begingroup
\lstset{
  language=HTML,
  alsoletter={-},
  otherkeywords={grid-row, grid-column, opacity, display, inline-grid},
  emph={stack, name}, % not working because of tag option
  identifierstyle=,
  morecomment=[s]{/*}{*/}
}
\lstinputlisting[caption={HTML source code illustrating a name stack},label=lst:html]{stack.html}
\endgroup

A final issue is that overlapping name stacks are not easy to read.
It may be possible to write names in a way that has no first name
but still makes all names clearly readable.
For example, a circle has no beginning or end, so arranging the names
in a circular pattern avoids arranging any author ``first''.
Figure~\ref{fig:circles} shows some initial experiments in this direction.
It remains unsolved how to fit such circular arrangements
in with the rest of a text document, which feels inherently sequential.
Circular arrangements also seem difficult to apply to small numbers of
authors such as $2$.

@@

@@
